Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-07-25 tex/background.tex
minor fix
add roache citation

Verification and validation of computational models---often abbreviated V\&V and viewed in concert---has developed into a mature subject with more than two decades of organized efforts to standardize it, dedicated conferences, and a  journal. 
The American Society of Mechanical Engineers (ASME), a standards-developing organization, formed its first Verification and Validation committee (known as V\&V 10) in 2001, with the charter: 
``to develop standards for assessing the correctness and credibility of modeling and simulation in computational solid mechanics.''
It approved its first document in 2006: The Guide for Verification and Validation in Computational Solid Mechanics (known as V\&V 10-2006). 
The fact that this guide was five years in the making illustrates just how complex the subject matter, and building consensus about it, can be. 
Since that first effort, six additional standards sub-committees have tackled V\&V in a variety of contexts. 
V\&V 70 is the latest, focused on machine-learning models.
The key principles laid out in the first V\&V standard persevere through the many subsequent efforts that have operated to this day. 
They are:

@@

The process of \emph{verification} establishes that a computational model correctly describes the intended mathematical equations and their solutions.
It encompasses both code correctness, and solution accuracy.
\emph{Validation}, on the other hand, seeks to determine to which measure a computational model represents the physical world. 
We like to say that ``verification is solving the equations right, and validation is solving the right equations'' (source unknown). 
But in reality the exercise can be much more complicated than this sounds. 
Computational models in most cases are built in a hierarchy of simplifications and approximations, and comparing with the physical world means conducting experiments, which themselves carry uncertainties.

@@

When studying both surface phonon polaritons and surface plasmon resonances, we can analyze the spectrums by measuring different quantities. 
We can measure scattering cross-section, extinction cross-section (scattering plus absorption), as well as reflection. 
These different approaches are comparable since the \textit{quantity of interest} is the wavelength/frequency at which the resonance modes happen. 
Whether we measure reflection or extinction cross-section, the wavelength (frequency) at which the peaks happen remains the same. 
Throughout this work, we will concentrate on studying the wavelength (frequency) at which the resonance modes occur, 
and we aim to replicate results from Rockstuhl et al.\ 2005 \cite{rockstuhl2005} and from Ellis et al.\ 2016 \cite{ellis2016}, 
and to validate our software against experimental results from Ellis et al.\ 2016 \cite{ellis2016}.

>>>>

Verification and validation of computational models---often abbreviated V\&V and viewed in concert---have developed into a mature subject with more than two decades of organized efforts to standardize it, dedicated conferences, and a  journal. 
The American Society of Mechanical Engineers (ASME), a standards-developing organization, formed its first Verification and Validation committee (known as V\&V 10) in 2001, with the charter: 
``to develop standards for assessing the correctness and credibility of modeling and simulation in computational solid mechanics.''
It approved its first document in 2006: The Guide for Verification and Validation in Computational Solid Mechanics (known as V\&V 10-2006). 
The fact that this guide was five years in the making illustrates just how complex the subject matter, and building consensus about it, can be. 
Since that first effort, six additional standards sub-committees have tackled V\&V in a variety of contexts. 
V\&V 70 is the latest, focused on machine-learning models.
The key principles laid out in the first V\&V standard persevere through the many subsequent efforts that have operated to this day. 
They are:

@@

The process of \emph{verification} establishes that a computational model correctly describes the intended mathematical equations and their solutions.
It encompasses both code correctness, and solution accuracy.
\emph{Validation}, on the other hand, seeks to determine to which measure a computational model represents the physical world. 
We like to say that ``verification is solving the equations right, and validation is solving the right equations'' \cite{roache1998}. 
But in reality the exercise can be much more complicated than this sounds. 
Computational models in most cases are built in a hierarchy of simplifications and approximations, and comparing with the physical world means conducting experiments, which themselves carry uncertainties.

@@

When studying both surface phonon polaritons and surface plasmon resonances, we can analyze the spectrums by measuring different quantities. 
We can measure scattering cross-section, extinction cross-section (scattering plus absorption), as well as reflection. 
These different approaches are comparable since the \textit{quantity of interest} is the wavelength (frequency) at which the resonance modes happen. 
Whether we measure reflection or extinction cross-section, the wavelength (frequency) at which the peaks happen remains the same. 
Throughout this work, we will concentrate on studying the wavelength (frequency) at which the resonance modes occur, 
and we aim to replicate results from Rockstuhl et al.\ 2005 \cite{rockstuhl2005} and from Ellis et al.\ 2016 \cite{ellis2016}, 
and to validate our software against experimental results from Ellis et al.\ 2016 \cite{ellis2016}.
